Equivalence Hypergraphs: E-Graphs for Monoidal Theories

### 2024-01-09 E-Hypergraphs-LICS24.tex
small addition Sec 5

\begin{remark}
Note that cospan 
\[
    n \xrightarrow{} l + j \xrightarrow{} C \xleftarrow{} r + i \xleftarrow{} k
\] is not necessarily well-typed.
The cospan's input internal interface may contain nodes that previously were a part of the output internal interface and similarly for output internal interface.

    The uniqueness and existence properties of boundary complements as defined above are discussed in the appendix (Proposition~\ref{prop:boundary_complement} and Proposition~\ref{prop:complement_existence}).

@@

if 
\begin{align*}    
    \mathcal{G} \xleftarrow{} n + k \Rrightarrow^{+} \mathcal{H} \xleftarrow{} n + k
\end{align*}
under the same rewrite rule.

>>>>

\begin{remark}
Note that cospan 
\[
    n \xrightarrow{} l + j \xrightarrow{} C \xleftarrow{} r + i \xleftarrow{} k
\] is not necessarily well-typed.
The cospan's input internal interface may contain nodes that previously were a part of the output internal interface and similarly for output internal interface.
\end{remark}

\begin{remark}
The uniqueness and existence properties of boundary complements as defined above are discussed in the appendix (Proposition~\ref{prop:boundary_complement} and Proposition~\ref{prop:complement_existence}).
\end{remark}

@@

if 
\begin{align*}    
    \mathcal{G} \xleftarrow{} n + k \Rrightarrow^{+} \mathcal{H} \xleftarrow{} n + k
\end{align*}
under the same rewrite rule.
We will use the same $\Rrightarrow^{+}$ and the concrete definition will be clear from the context.
